Common sense approaches to sharing tabular data alongside publication

### 2021-09-17 new-paper.Rmd
Fixed R1-3
Updated text
Fixed R2-3

Tools that can be used to prepare datasets and metadata (*the infrastructure*) and minimal sets of practices (*guidelines*) for reuse are sparse [@Arslan2019; @Roche2015]. Unlike code, datasets are far more diverse in terms of heterogeneity, size, and format. This makes them particularly challenging to standardize or easily "install" where the code is running. There have been some efforts to improve this process, such as gogetdata, the Dat Project, and the formation of a private company, Quilt.

@@

Journals provide data papers in a formal publication explaining data that is archived. This is a familiar avenue for researchers to receive credit and citation. Writing a data paper can be very useful for researchers, but, data papers lack guidelines on how to structure data for effective reuse and sharing. Partner with Dryad to link archived data with research papers. We recommend partnering with best practice data repositories that emphasize curation, like Dryad. This way the data will have a long-term archiving and will also have professional curation to ensure that the published data are usable and have enough metadata to be understood. While writing a data paper can be very useful for researchers, journals that publish data papers lack guidelines on how to structure data for effective reuse and sharing. Data journals should routinely be partnering with best practice repositories to best support the underlying data.

>>>>

Tools that can be used to prepare datasets and metadata (*the infrastructure*) and minimal sets of practices (*guidelines*) for reuse are sparse [@Arslan2019; @Roche2015]. Unlike code, datasets are far more diverse in terms of heterogeneity, size, and format. This makes them particularly challenging to standardize or easily "install" where the code is running. There have been some efforts to improve this process, such as gogetdata, the Dat Project, Frictionless Data [@Fowler_Barratt_Walsh_2018], and the formation of a private company, Quilt.

@@

Journals provide data papers in a formal publication explaining data that is archived (e.g. Ecology, Scientific Data). This is a familiar avenue for researchers to receive credit and citation. Writing a data paper can be very useful for researchers, but, data papers lack guidelines on how to structure data for effective reuse and sharing. We recommend partnering with best practice data repositories that emphasize curation, like Dryad. This way the data will have a long-term archiving and will also have professional curation to ensure that the published data are usable and have enough metadata to be understood. While writing a data paper can be very useful for researchers, journals that publish data papers lack guidelines on how to structure data for effective reuse and sharing. Data journals should routinely be partnering with best practice repositories to best support the underlying data.
